\thispagestyle{empty}
\begin{raggedleft}
\vspace*{23mm}
\hfill {\huge {\bf {Acknowledgements}}} \\
\vspace{6mm}
\hfill \rule{4in}{.015in} \\
\vspace{19mm}
\end{raggedleft}


\noindent{I acknowledge William Hartley, for the support provided in the past two years, as mentor in galaxy evolution studies and research life. I am so thankful to my supervisor Ofer Lahav, for what he taught me over the years, while also leaving space for my own research interests, and for always understanding my problems. I acknowledge the DES Fermilab team and the URA visiting scholar award for allowing me to do research at Fermilab, broaden my research horizons and opening precious opportunities for my future. In particular, I am grateful to Marcelle Soares--Santos and James Annis for being the best hosts possible during my stay at Fermilab and for introducing me to the world of gravitational waves. I also thank the whole DES collaboration for providing an extremely stimulating environment for science, but also a relaxed and even often fun atmosphere. Each single DES collaboration meeting has been an extremely stressful moment in which I also clearly remembered how much passion I have for this work. I am extremely grateful to my family, my mum, dad and brother, for the support and help always provided, especially in the darkest moments. I acknowledge all my colleagues and fellow or former PhD students at UCL, Luisa Lucie-Smith, Felix Priestley, Guido Roberts-Borsani, Boris Leistedt, Davide Gualdi, Ingo Waldmann, Nicola Baccichet, Marco Rocchetto, Daniela Saadeh, David Buckley, Paul Moseley, Stephanie Jouvel, David Johnson for making my everyday research life at UCL brighter. I acknowledge UCL for providing such a stimulating, bright and open--minded environment to work in. I acknowledge the UCL Women's Volleyball team and the UCL Elite athlete programme, which gave me the honour to represent my university and compete at high level. I acknowledge my long-time friends Elisabetta Mutidieri, Francesca Ussia, Chiara Grillo, Debora Grillo, Isabella Cuoghi, Lewis Saccocci, Federica Ferretti for being always close even when we have been far away. I acknowledge my newest and closest friends, Edoardo Mortari, Garth Oates and Chlo\"{e} Donegan for making me enthusiastic about my life in the UK again. I acknowledge who abandoned me and made me the stronger woman I am now, so that I could be able to reach my goals despite the obstacles. I also thank the sports teams and communities that have been such an important part of my life throughout these years. I would like to thank London Orcas, for being such an amazing family to me for two years, and coach Jalal, the best indoor volleyball coach I have ever had. I am grateful to world--wide famous beach volleyball coach Marco Solustri, who made me a much stronger beach volleyball player in just one season. I thank my beach volleyball partners from the past beach volleyball seasons, for their love and patience with me inside and outside the court: Michela Pessotto, Carolina Pi\~{n}a, Danae Filioti, Katja Gless, Chiara Kleinsasser. I also thank coaches Andrea Zurini, Stefano Picariello, Roberto Viscuso and Daniela Gattelli for making me feel always welcome to train and part of the Italian beach volleyball community after I left my country. I acknowledge Arianna Tallarita and Anna Valsi for being such fun friends and beach volleyball partners back in Rome. A big thank you goes to Team One Volleyball club and Progression Volleyball in Chicagoland, that welcomed me in the US volleyball world and allowed me to train and play with the top athletes in Illinois, transforming the cold winter I spent there into a great experience. Thank you to coaches Taye Im and Brian McDermand, to those great players and friends that are Lara Janson, Courtney Baleiko, Amy Nicole, Sam Crankshaw, Erin O'Connor, Candice McNally, Dorey Gray. I am finally very grateful to CrossFit Evolving, Engine Room CrossFit, Crossfit MOS and in particular coach Spud Nicholson for keeping my life active and push my limits in sports even during my busiest thesis writing times.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% If you have more than one page in your acknowledgements, include the
% following on each page after the first:
%
% \thispagestyle{fancyplain}
% \lhead[\fancyplain{}{\vspace{4mm}\thepage \vspace{0mm}}]{}
% \rhead[]{\fancyplain{}{\vspace{4mm}\thepage \vspace{0mm}}}
% \cfoot{}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

