\thispagestyle{empty}

\vspace*{3cm}

\begin{flushleft}
I, Antonella Palmese, confirm that the work presented in this thesis is my own. Where
information has been derived from other sources, I confirm that this has been indicated in
the thesis. In particular I note these contributions:
\begin{itemize}
\item The work presented in Chapter 2 has been published with the DES Science Verification data release at \url{https://des.ncsa.illinois.edu/releases/sva1}, ANNz2 has been written by Iftach Sadeh, Ofer Lahav and Filipe Abdalla, the BMA code has been written by James Annis and myself. I have worked closely with Iftach Sadeh on testing ANNz2 and providing DES Science Verification photo-$z$'s catalogues.
\item The work presented in Chapter 3 has been published in \citet{palmese17}. \textsc{GalFit} runs have been performed by Federica Tarsitano and William Hartley, pixel color magnitude diagrams have been produced by Chris Conselice. The DES gravitational wave follow up program involves the effort of a whole team composed by a dozen people. The host matching work has been performed with the help of DES Supernovae experts. The whole pipeline is shortly described in \citet{herner}, and has been used in the analysis of GW170814, which will soon be published in Doctor et al. (2018). My contribution to the DECam GW follow up work partially described in this chapter has granted me co-authorship in \citet{MMApaper}, \citet{gw170817h0}, \citet{marcelle17}, \citet{scolnic} and \citet{Cowperthwaite}.
\item The work presented in Chapter 4 has been published in \citet{palmese16}.
\item The work presented in Chapter 5 will shortly be published in Palmese et al. (2018) and Welch et al. (2018). Palmese et al. (2018) is currently undergoing the DES review process required for submission. The membership probability assignment work has been led by Brian Welch, with major contribution by James Annis, Huan Lin, Marcelle Soares--Santos and myself. The weak lensing mass calibration section is part of work that has been published in \citet{maria}, who lead the work with contributions by the same team.
\item The work presented in Chapter 6 will also shortly be published in Palmese et al. (2018). In the last sections I present work on Intra--cluster light, which has been lead by Yuanyuan Zhang and to which I gave major contributions. This work is undergoing the DES review process and will shortly be published in Zhang, Yanny, Palmese et al. (2018). The work on the effect of the Intra--cluster light on photo-$z$ has been lead by Daniel Gruen in particular for what concerns the weak lensing formalism, and will shortly be published in Gruen, Zhang, Palmese et al. (2018).
\end{itemize}
\end{flushleft}